### 2019-12-23 defesa/tex/chapter/e3p.tex
wip

We refer to this problem as \sigla{E3PNT}{Ellipse by Three points}, and an instance of it is given by three points $u, v, w \in \R^2$ and $E$, the coverage area of an ellipse with shape parameters $(a, b) \in \R^2_{>0}$, with $a > b$. A solution of E3PNT is a pair $(q, \theta) \in \R^2\times[0, \pi)$, such that $\{u, v, w\} \subset \partial E(q, \theta)$. As a last remark, because of its application on \autoref{chapter:ellipses_n}, we need to encounter every solution of E3PNT, this requirement, of course, makes the problem more challenging.

@@

To make it simpler, let us translate the system, so the point $u$ is at $(0,0)$. Then, we assume that the ellipse is actually axis-parallel and the points are the ones rotating. When an angle is found such that the three points lie on the border of the axis-parallel ellipse, a linear transformation can be applied to compress the x-axis by $\frac{b}{a}$, transforming the ellipse into a circle of radius $b$. This transformation can be seen on \autoref{fig:circumscribed-circle} where a solution of the E3PNT is transformed into a solution of the problem of finding a circumscribed circle of a triangle. 
This process can be parametrized by the angle of rotation of the points, as described by \autoref{eq:trpnts}, and because of the invertibility of linear transformations, solutions for E3PNT can be obtained by reversing these transformations.

\begin{figure}
	\centering
	\caption{Transforming an ellipse into a circle. T1, T2, and T3 represent the steps of the transformation.}
	\includegraphics{tex/figures/scripts/circumscribed-circle}
	\fautor
	\label{fig:circumscribed-circle}
\end{figure}
\begin{equation}\label{eq:trpnts}
\varphi(p, \theta)=\left[\begin{array}{cc}
\frac{b}{a}&0\\
0&1
\end{array}\right]
\left[\begin{array}{cc}
\cos{\theta}&\sin{\theta}\\
-\sin{\theta}&\cos{\theta}
\end{array}\right]\left[\begin{array}{c}
p_x\\
p_y
\end{array}\right].
\end{equation}

@@

It turns out that for three non-colinear fixed points, there is always an unique circumscribed circle. Also, finding this unique circle can be done analytically, hence its radius can be easily computed and compared to $b$ when an angle is given.
Let $A(\theta)$ be the area of the triangle formed by the points $\{(0, 0), \varphi(v, \theta), \varphi(w, \theta)\}$--note that the transformation does not preserve distance or area. Then, the radius $R$ of the circumscribed circle is given by \autoref{eq:circumscribed_circle} \cite[p.~189]{johnson1960}.

\begin{equation}\label{eq:circumscribed_circle}
R = \dfrac{\norm{\varphi(v, \theta)}\norm{\varphi(w, \theta)}\norm{\varphi(v, \theta)-\varphi(w, \theta)}   }{4A(\theta)}.
\end{equation}

Imposing the radius to be equal $b$ and squaring to eliminate the square roots present in the Euclidean distance, a function $\xi : [0, 2\pi) \mapsto \mathbb{R}_{>0}$ is defined by \autoref{eq:circumscribed_circle_b} in such a way that its zeros determine solutions to the E3PNT's instance. Two questions about $\xi(\theta)$ that arise are: is its set of roots finite? And, can they be found analytically?

\begin{equation}\label{eq:circumscribed_circle_b}
\xi(\theta) = 16b^2A(\theta)^2 - \norm{\varphi(v, \theta)}^2\norm{\varphi(w, \theta)}^2\norm{\varphi(v, \theta)-\varphi(w, \theta)}^2.
\end{equation}

@@

One of the steps of the method developed on \autoref{chapter:ellipses_n} is to iterate over every solution of E3PNT for every triplet of points. Of course doing that is only possible for a finite number of solutions. Also, discovering a bound for that is essential for determining the efficiency of the algorithm.

Back on \autoref{chapter:definitions} real trigonometric polynomials were introduced. It was stated that a $n$-degree polynomial can have up to $2n$ distinct roots. It turns out that $\xi$ is a real trigonometric polynomial of degree $6$ and it can be written in the format given by \autoref{eq:trig_poly_2} which implies that it can have up to $12$ distinct roots.
 To show that, just note that it is possible to write $\norm{\varphi(v, \theta)}^2$ and $A(\theta)^2$ in that form, as it can be seen on \autoref{eq:dd} and \autoref{eq:dd2}. It is also possible to see that the term of higher the degree of $\xi$ is the multiplication of the three squared distances. As $\norm{\varphi(v, \theta)}^2$ has degree $2$, the degree of $\xi$ is $6$.
\begin{align}\label{eq:dd}
	\norm{\varphi(v, \theta)}^2 = (v_x\frac{b}{a}\cos\theta + v_y\frac{b}{a}\sin\theta)^2 + (v_y\cos\theta - v_x\sin\theta)^2\\
	\label{eq:dd2} A(\theta)^2=\dfrac{1}{4}\det\left(
	\begin{array}{cc}
		v_x\frac{b}{a}\cos\theta + v_y\frac{b}{a}\sin\theta&v_y\cos\theta - v_x\sin\theta\\
		w_x\frac{b}{a}\cos\theta + w_y\frac{b}{a}\sin\theta&w_y\cos\theta - w_x\sin\theta
	\end{array}\right)^2
\end{align}

@@

The idea of this approach was to use the six-parameter conic equation to represent an ellipse. This equation is given by \autoref{eq:gen_ellipse}.

\begin{equation}\label{eq:gen_ellipse}
Ax^2+Bxy+Cy^2+Dy+Ex+F=0.
\end{equation}
This equation actually represents any conic, for it to be an ellipse the condition $B^2 -4AC < 0$ must be satisfied.

Setting the first point to be the origin, we get $F=0$, using the other two points, it is possible to write $D$ and $E$ in terms of $A, B, C$. As any multiple of \autoref{eq:gen_ellipse} represents the same conic, we can set $B$ to be equal $1$. Then, we end up with two variables, $A$ and $C$, and still need to impose that the final equation represents an ellipse and its major-axis and minor-axis have the predefined value. Let $\Delta=4AC-B^2=4AC-1$, \autoref{eq:gen_ellipse_a} and \autoref{eq:gen_ellipse_b} for both major-axis and minor-axis respectively, assuming $F=0$.

\begin{align}\label{eq:gen_ellipse_a}
a^2 = \dfrac{2\dfrac{AE^2 -BDE +CD^2}{\Delta}}{A + C - \sqrt{1 + (A-C)^2}}\\
\label{eq:gen_ellipse_b}b^2 = \frac{2\dfrac{AE^2 -BDE +CD^2}{\Delta}}{A + C + \sqrt{1 + (A-C)^2}}
\end{align}

These two equations define two curves in $\R^2$ with $A$ and $C$ being the chosen variables. The solutions lie in the set of intersection of these curves. Finding this set was judged to be non-trivial and probably could be approximated numerically, however, we decided not to further pursue this approach.

@@

One of the most useful techniques when dealing with complicated functions is approximation. They appear in various methods whenever a derivative or integral needs to be calculated or for example, in our case, when the roots of a function need to be determined. In general, one has a function $f$ that is part of a family of functions $\mathcal{A}$ and wants to select a simpler function $f^*$ from a set of functions $\mathcal{A^*}$, such that $f^*$ is close enough to $f$ \cite[p.~3]{powell}. For this problem, the approximation of $\xi(\theta)$ on the interval $[0, \pi)$ is considered. The approximation set of functions is going to be the set of $n$-degree Chebyshev polynomials which the roots can be found through determining the eigenvalues of a $n$ by $n$ matrix.

@@

Chebyshev polynomials are widely used in Numerical Analysis in areas like numerical integration, polynomial approximation, and ordinary and partial differential equations.
They are also very useful in practice and are present in extension libraries in Python and MATLAB.

@@

We refer to $T_n : [-1, 1] \mapsto [-1, 1]$ as the $n$-degree Chebyshev polynomial of the first kind, and it is defined as follows:

\begin{equation}
T_n(x) = \cos({n\arccos x})
\end{equation}

It is important to mention that this definition can be extended to the whole real line. Using some trigonometric identities, $T_n$ can also be expressed as a recurrence relation:

\begin{equation}
T_n(x) = 2xT_{n-1}(x) - T_{n-2}(x).
\end{equation}

An important property worth bringing up is that Chebyshev polynomials are orthogonal and form a basis for the polynomial space. This implies that any $p_n$ of degree up to $n$ can be expressed as a truncated Chebyshev series:

\begin{equation}\label{eq:chebseries}
p_n(x) = \sum_{j=0}^{n} a_j T_j(x).
\end{equation}

@@

To choose the degree of the interpolation we use the last coefficient rule-of-thumb introduced by \citeonline[p.~50]{boyd:2001}. There is no guarantee that this method will choose $n$, such that $f_n$ is close enough to $\xi$ everywhere on $[0, \pi)$, nonetheless, in practice, it is taken to be a good estimate for the error $r_n$:
\begin{equation}
r_n = \max_{0 \le \theta \le \pi} |f_n(\theta) - \xi(\theta)|.
\end{equation}

@@

It is possible to make another reduction to obtain a degree-$6$ polynomial, this can lower the size of the companion matrix utilized on obtaining the roots of $h$ from $12^2=144$ to $6^2=36$.
As it has been mentioned before, an ellipse is symmetric with respect to its own major or minor axis. 
In other words, rotating an ellipse by $\theta \in [0, \pi)$ is the same as rotating the same ellipse by $\pi + \theta$.
On the other hand, on \autoref{chapter:definitions}, it was stated that the angle of the complex numbers $z$ and $-z$ has the same symmetry with each other as the aforementioned symmetry of ellipses:
\begin{equation*}
angle(-z) = \pi + angle(z).
\end{equation*}
From that, as $g(e^{i\theta})=\xi(\theta)$ for every $\theta \in [0, 2\pi)$, we conclude that $g(-z)=g(z)$. This implies that $h$ is, in fact, an even polynomial, or that $h(-z) = h(z)$ is true for every $z\in\mathbb{C}$:
\begin{align}
h(-z) = (-z)^6g(-z) = z^6g(z).
\end{align}
Therefore, all the odd degree coefficients of $h$ are $0$ and we can define the $6$-degree polynomial $f : \mathbb{C} \mapsto \mathbb{C}$ with the substitution $y=z^2$:
\begin{equation}
f(y) = \sum_{k=0}^{6} c_{2k} y^k.
\end{equation}
Then from every root $\hat{y}$ of $f$, two roots of $h$ can be obtained: $\sqrt{\hat{y}}$ and $-\sqrt{\hat{y}}$. As the angle of $-\sqrt{\hat{y}}$ is not between $[0, pi)$ we can ignore it. Note that the the square root of $\hat{y}$ does not need to be calculated, as only the angles are needed and they can be obtained by:
\begin{equation}
angle(\sqrt{z}) = angle(z)/2.
\end{equation}
Finally, using the QR algorithm mentioned on \autoref{chapter:definitions} a $\bigO(n^3)$ algorithm can be constructed for E3P. Because $n$ will always be $6$, we can say that we have a $\bigO(1)$ algorithm.

It is also worth mentioning that a pattern on the coefficients of $f$ was identified, and maybe for future work it can be used for further improvements. Analyzing the polynomials produced for several instances, the following seems to be true:
\begin{equation}
c_k = \overline{c_{6-k}},
\end{equation}
for $k=0, \dots, 6$. For now, we do not have any ideas on how it could be proved. Nevertheless, this seems to lead somewhere interesting because this condition guarantees that $f$ is a self-reciprocal polynomial which implies that its roots will always come in pairs $(\hat{z}, 1/\hat{z})$.

>>>>

\section{Definition}

We call the problem introduced in this section \sigla{E3PNT}{Ellipse by Three points}. An instance of it is given by three points $u, v, w \in \R^2$ and the shape parameters of an ellipse $(a, b) \in \R^2_{>0}$, with $a > b$.

Let $E$ be the coverage area of an ellipse with the given shape parameters $(a, b)$, then a solution of E3PNT is a pair $(q, \theta) \in \R^2\times[0, \pi)$, such that $\{u, v, w\} \subset \partial E(q, \theta)$. As a last remark, because of its application on \autoref{chapter:ellipses_n}, it is only useful a method would only be useful to our case if it can encounter every solution of E3PNT. This requirement, of course, makes the problem more challenging.

@@

To make it simpler, let us translate the system, so the point $u$ is at $(0,0)$. Then, we assume that the ellipse is actually axis-parallel and the points are the ones rotating. When an angle is found such that the three points lie on the border of the axis-parallel ellipse, a linear transformation can be applied to compress the x-axis by $\frac{b}{a}$, transforming the ellipse into a circle of radius $b$. This transformation can be seen on \autoref{fig:circumscribed-circle} where a solution of the E3PNT is transformed into a solution of the problem of finding a circumscribed circle of a triangle. 
This process can be parametrized by the angle of rotation of the points, as described by

\begin{equation}\label{eq:trpnts}
\varphi(p, \theta)=\left[\begin{array}{cc}
\frac{b}{a}&0\\
0&1
\end{array}\right]
\left[\begin{array}{cc}
\cos{\theta}&\sin{\theta}\\
-\sin{\theta}&\cos{\theta}
\end{array}\right]\left[\begin{array}{c}
p_x\\
p_y
\end{array}\right],
\end{equation}
because of the invertibility of linear transformations, solutions for E3PNT can be obtained by reversing these transformations.

\begin{figure}
	\centering
	\caption{Transforming an ellipse into a circle. T1, T2, and T3 represent the steps of the transformation.}
	\includegraphics{tex/figures/scripts/circumscribed-circle}
	\fautor
	\label{fig:circumscribed-circle}
\end{figure}

@@

It turns out that for three non-colinear fixed points, there is always an unique circumscribed circle. Also, finding this unique circle can be done analytically, and its radius $R$ can be computed through the expression
\begin{equation}\label{eq:circumscribed_circle}
R = \dfrac{\norm{\varphi(v, \theta)}\norm{\varphi(w, \theta)}\norm{\varphi(v, \theta)-\varphi(w, \theta)}   }{4A(\theta)},
\end{equation}
with $A(\theta)$ being the area of the triangle formed by the points $\{(0, 0), \varphi(v, \theta), \varphi(w, \theta)\}$--note that the transformation does not preserve distance or area. For more details about \autoref{eq:circumscribed_circle} see \citeonline[p.~189]{johnson1960}.

Imposing the radius to be equal $b$ and squaring to eliminate the square roots present in the Euclidean distance, a function $\xi : [0, 2\pi) \mapsto \mathbb{R}_{>0}$ is defined as 
\begin{equation}\label{eq:circumscribed_circle_b}
\xi(\theta) = 16b^2A(\theta)^2 - \norm{\varphi(v, \theta)}^2\norm{\varphi(w, \theta)}^2\norm{\varphi(v, \theta)-\varphi(w, \theta)}^2,
\end{equation}
in such a way that its zeros determine solutions for E3PNT.

Lastly, two questions about $\xi(\theta)$ that arise are: is its set of roots finite? And, if its set of roots is finite, can they be found analytically?

@@

One of the steps of the method developed on \autoref{chapter:ellipses_n} is to iterate over every solution of E3PNT for every triplet of points. Of course doing that is only possible for a finite number of solutions. Also, given that it is limited, discovering a bound for it is essential for determining the efficiency of the algorithm.

Back on \autoref{chapter:definitions} real trigonometric polynomials were introduced. It was stated that a $n$-degree polynomial can have up to $2n$ distinct roots. It turns out that $\xi$ is a real trigonometric polynomial of degree $6$ and it can be written in the format given by \autoref{eq:trig_poly_2} which implies that it can have up to $12$ distinct roots.
 To show that, just note that it is possible to write $\norm{\varphi(v, \theta)}^2$ and $A(\theta)^2$ in that form
 \begin{align}\label{eq:dd}
 	\norm{\varphi(v, \theta)}^2 = (v_x\frac{b}{a}\cos\theta + v_y\frac{b}{a}\sin\theta)^2 + (v_y\cos\theta - v_x\sin\theta)^2\\
 	\label{eq:dd2} A(\theta)^2=\dfrac{1}{4}\det\left(
 	\begin{array}{cc}
 		v_x\frac{b}{a}\cos\theta + v_y\frac{b}{a}\sin\theta&v_y\cos\theta - v_x\sin\theta\\
 		w_x\frac{b}{a}\cos\theta + w_y\frac{b}{a}\sin\theta&w_y\cos\theta - w_x\sin\theta
 	\end{array}\right)^2.
 \end{align}
  It is also possible to see that the term of higher the degree of $\xi$ is the multiplication of the three squared lengths of the triangle formed by the points $\{(0, 0), \varphi(v, \theta), \varphi(w, \theta)\}$. This multiplication has the same degree of $(\norm{\varphi(v, \theta)}^2)^3$, and because $\norm{\varphi(v, \theta)}^2$ has degree $2$, the degree of $\xi$ is $6$.

@@

The idea of this approach was to use the six-parameter conic equation to represent an ellipse. This equation is given by
\begin{equation}\label{eq:gen_ellipse}
Ax^2+Bxy+Cy^2+Dy+Ex+F=0.
\end{equation}
This equation actually represents any conic, for it to be an ellipse the condition $B^2 -4AC < 0$ must be satisfied.

Setting the first point to be the origin, we get $F=0$, using the other two points, it is possible to write $D$ and $E$ in terms of $A, B, C$. As any multiple of \autoref{eq:gen_ellipse} represents the same conic, we can set $B$ to be equal $1$. Then, we end up with two variables, $A$ and $C$, and still need to impose that the final equation represents an ellipse and its major-axis and minor-axis have the predefined value. Let $\Delta=4AC-B^2=4AC-1$, and assume $F=0$, then the expressions for both major-axis and minor-axis respectively are
\begin{align}\label{eq:gen_ellipse_a}
a^2 = \dfrac{2\dfrac{AE^2 -BDE +CD^2}{\Delta}}{A + C - \sqrt{1 + (A-C)^2}}\\
\label{eq:gen_ellipse_b}b^2 = \frac{2\dfrac{AE^2 -BDE +CD^2}{\Delta}}{A + C + \sqrt{1 + (A-C)^2}}.
\end{align}
These two equations define two curves in $\R^2$ with $A$ and $C$ being the chosen variables. The solutions lie in the set of intersection of these curves. Finding this set was judged to be non-trivial and probably could be approximated numerically, however, we decided not to further pursue this approach.

@@

One of the most useful techniques when dealing with complicated functions is approximation. They appear in various methods whenever a derivative or integral needs to be calculated or for example, in our case, when the roots of a function need to be determined. In general, one has a function $f$ that is part of a family of functions $\mathcal{A}$ and wants to select a simpler function $f^*$ from a set of functions $\mathcal{A^*}$, such that $f^*$ is close enough to $f$ \cite[p.~3]{powell}. For this problem, the approximation of $\xi(\theta)$ on the interval $[0, \pi)$ is considered. The approximation set of functions is going to be the set of $n$-degree Chebyshev polynomials which the roots can be found through determining the eigenvalues of a $n\times n$ matrix.

@@

Chebyshev polynomials are widely used in Numerical Analysis in areas like numerical integration, polynomial approximation, and ordinary and partial differential equations.
They are also very useful in practice and are present in extension libraries in Python, MATLAB and C.

@@

We refer to $T_n : [-1, 1] \mapsto [-1, 1]$ as the $n$-degree Chebyshev polynomial of the first kind, and it is defined as
\begin{equation}
T_n(x) = \cos({n\arccos x}).
\end{equation}
It is important to mention that this definition can be extended to the whole real line. Using some trigonometric identities, $T_n$ can also be expressed as a recurrence relation
\begin{equation}
T_n(x) = 2xT_{n-1}(x) - T_{n-2}(x).
\end{equation}

An important property worth bringing up is that Chebyshev polynomials are orthogonal and form a basis for the polynomial space. This implies that any $p_n$ of degree up to $n$ can be expressed as a truncated Chebyshev series
\begin{equation}\label{eq:chebseries}
p_n(x) = \sum_{j=0}^{n} a_j T_j(x).
\end{equation}

@@

To choose the degree of the interpolation we use the last coefficient rule-of-thumb introduced by \citeonline[p.~50]{boyd:2001}. There is no guarantee that this method will choose $n$, such that $f_n$ is close enough to $\xi$ everywhere on $[0, \pi)$, nonetheless, in practice, it is taken to be a good estimate for the error $r_n$:
\begin{equation}
r_n = \max_{0 \le \theta < \pi} |f_n(\theta) - \xi(\theta)|.
\end{equation}

@@

It is possible to make another reduction to obtain a degree-$6$ polynomial, this can lower the size of the companion matrix utilized on obtaining the roots of $h$ from $12^2=144$ to $6^2=36$.
As it has been mentioned before, an ellipse is symmetric with respect to its own major or minor axis. 
In other words, rotating an ellipse by $\theta \in [0, \pi)$ is the same as rotating the same ellipse by $\pi + \theta$.
On the other hand, on \autoref{chapter:definitions}, it was stated that the angle of the complex numbers $z$ and $-z$ has the same symmetry with each other as the aforementioned symmetry of ellipses:
\begin{equation*}
angle(-z) = \pi + angle(z).
\end{equation*}
From that, as $g(e^{i\theta})=\xi(\theta)$ for every $\theta \in [0, 2\pi)$, we conclude that $g(-z)=g(z)$. This implies that $h$ is, in fact, an even polynomial, or that $h(-z) = h(z)$ is true for every $z\in\mathbb{C}$:
\begin{align}
h(-z) = (-z)^6g(-z) = z^6g(z).
\end{align}
Therefore, all the odd degree coefficients of $h$ are $0$ and we can define the $6$-degree polynomial $f : \mathbb{C} \mapsto \mathbb{C}$ with the substitution $y=z^2$:
\begin{equation}
f(y) = \sum_{k=0}^{6} c_{2k} y^k.
\end{equation}
Then from every root $\hat{y}$ of $f$, two roots of $h$ can be obtained: $\sqrt{\hat{y}}$ and $-\sqrt{\hat{y}}$. As the angle of one of the roots will not be between $[0, \pi)$ we can ignore on of them. 
Note that the the square root of $\hat{y}$ does not need to be calculated, as only the angles are needed and they can be obtained by:
\begin{equation}
angle(\sqrt{z}) = angle(z)/2.
\end{equation}
Finally, using the QR algorithm mentioned on \autoref{chapter:definitions} a $\bigO(n^3)$ algorithm can be constructed for E3P. Because $n$ will always be $6$, we can say that we have a $\bigO(1)$ algorithm.

It is also worth mentioning that a pattern on the coefficients of $f$ was identified, and maybe for future work it can be used for further improvements. Analyzing the polynomials produced for several instances, the following seems to be true:
\begin{equation}\label{eq:palindromic_pol}
c_k = \overline{c_{6-k}},
\end{equation}
for $k=0, \dots, 6$. For now, we neither have any ideas on how \autoref{eq:palindromic_pol} could be proved nor how it could be used for further improving our algorithm.

### 2019-12-23 defesa/tex/chapter/introducao.tex
wip

One of the 21 Karp's NP-Complete problems\footnote{The decision version, which asks if there is a cover of size $k$, is NP-Complete.} \cite{karp}, the Minimum Cover Problem is very well explored and considered to be a classic. 
Given a demand set along with a collection of subsets of the demand set. The problem is then to determine the minimum number of elements from the collection of subsets that are needed to cover the whole demand set. One of its most famous examples is the Minimum Vertex Cover defined over graphs, where the vertex set has to be covered by a subset of edges.

The second type of covering problems arose from the fact that covering almost all the demand set can be a lot cheaper than having to cover it all \cite{garcia}. This second type is known as \sigla{\MCLP}{Maximum Covering Location Problem}\footnote{Originally, the problem was defined using the word \textit{Maximal} on its title. In some sources, however, the word \textit{Maximum} is adopted.} and was introduced in \citeonline{church:1974}.

In this first study, the author defined the problem on graphs with the demand being a subset of the graph's vertices. Given a facility set where each facility has a coverage radius, the objective was then to maximize the coverage of the demand set by choosing vertices to place each facility.

@@

In \citeonline{church:1984} a new kind of MCLP named \sigla{\PMCLP}{Planar Maximum Covering Location Problem} was introduced. Unlike its predecessor, this version of the problem was not defined on a network. Instead, on PMCLP the demand set and the facilities are located in $\R^2$ and a facility's coverage area is determined by a distance function. 
Initially, the Euclidean distance was considered and the idea behind the method proposed in \citeonline{church:1984} was to convert PMCLP into an instance of MCLP and then utilize any of the previous developed exact methods to obtain a solution for PMCLP. This reduction was done by identifying a \sigla{CLS}{Candidate Locations Set} which represented the possible locations that needed to be evaluated for every facility, such that the optimal solution could be found. From the CLS, a network was built on which MCLP could be applied. Generating the CLS specifically for the case of Euclidean distance will be described here on \autoref{chapter:pmclp}.

@@

Two versions of PMCLP are studied in this work, both of them related to ellipses. The first one was introduced in \citeonline{canbolat} and will be referred to here as \sigla{PMCE}{Planar Maximum Covering by Ellipses}. This version does not allow the ellipses to rotate, so basically it only differs from its disks counterpart in the shape of the facility's coverage area. The second version was introduced in \citeonline{andreta} and will be referred to here as \sigla{PMCER}{Planar Maximum Covering by Ellipses with Rotation}. This version of the problem had no restriction on the rotation of ellipses--note that this is a slightly bigger modification of PMCLP compared to the first one, as not only the location for the facilities must be determined, but also their angle of rotation.
The main motivation to study these two versions of PMCLP is that cellphone towers can have elliptically shaped coverage area, therefore, to determine what are the best locations to place $m$ cellphone towers to maximize the amount of the population covered by their signal, an elliptical PMCLP is better-suited \cite{canbolat}.

>>>>

One of the 21 Karp's NP-Complete problems\footnote{The decision version, which asks if there is a cover of size $k$, is NP-Complete.} \cite{karp}, the Minimum Cover Problem is very well explored and considered to be a classic. 
Given a demand set along with a collection of subsets of the demand set, the problem is to determine the minimum number of elements from the collection of subsets that are needed to cover the whole demand set. One of its most famous examples is the Minimum Vertex Cover defined over graphs, where the vertex set has to be covered by a subset of edges.

The second type of covering problems arose from the fact that covering almost all the demand set can be a lot cheaper than having to cover it all \cite{garcia}. This second type is known as \sigla{\MCLP}{Maximal Covering Location Problem} and was introduced in \citeonline{church:1974}.
In this first study, the author defined the problem on graphs with the demand being a subset of the graph's vertices. The objective was to maximize the coverage of the demand set by choosing the location of a given facility set on the graph.
Every facility had a given coverage radius, which meant that after it was placed on the graph, every vertex within that radius would be considered covered.

@@

In \citeonline{church:1984} a new kind of MCLP named \sigla{\PMCLP}{Planar Maximal Covering Location Problem} was introduced. Unlike its predecessor, this version of the problem was not defined on graphs. Instead, on PMCLP the demand set and the facilities are located in $\R^2$ and a facility's coverage area is determined by a distance function. 
Initially, the Euclidean distance was considered and the idea behind the method proposed in \citeonline{church:1984} was to convert PMCLP into an instance of MCLP and then utilize any of the previous developed exact methods to obtain a solution for PMCLP. This reduction was done by identifying a \sigla{CLS}{Candidate Locations Set} which represented the possible locations that needed to be evaluated for every facility, such that the optimal solution could be found. From the CLS, a network was built on which MCLP could be applied. Generating the CLS specifically for the case of Euclidean distance will be described here on \autoref{chapter:pmclp}.

@@

Two versions of PMCLP are studied in this work, both of them related to ellipses. The first one was introduced in \citeonline{canbolat} and will be referred to here as \sigla{PMCE}{Planar Maximal Covering by Ellipses}. This version does not allow the ellipses to rotate, so basically it only differs from its disks counterpart in the shape of the facility's coverage area. The second version was introduced in \citeonline{andreta} and will be referred to here as \sigla{PMCER}{Planar Maximal Covering by Ellipses with Rotation}. This version of the problem had no restriction on the rotation of ellipses--note that this is a slightly bigger modification of PMCLP compared to the first one, as not only the location for the facilities must be determined, but also their angle of rotation.
The main motivation to study these two versions of PMCLP is that cellphone towers can have elliptically shaped coverage area, therefore, to determine what are the best locations to place $m$ cellphone towers to maximize the amount of the population covered by their signal, an elliptical PMCLP is better-suited \cite{canbolat}.
